\documentclass[10pt,a4paper]{article}

%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is at http://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
\usepackage[T2A]{fontenc}
\usepackage[koi8-r]{inputenc}
\usepackage[russian,english]{babel}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\pagestyle{empty}

\begin{document}
\begin{center}

%% Title in English:
{\Large An asymptotic of a certain Riemann--Hilbert problem under singular deformation of a domain}

\bigskip


%% Author 1:
{\sc Sergey Bezrodnykh}

%% Address:
{\small\it Dorodnicyn Computing Centre, Moscow 119333, Russia}

%% Email:
{\small\rm sergeyib@pochta.ru}


\bigskip

%% Author 2:
{\sc Vladimir Vlasov}

{\small\it Dorodnicyn Computing Centre, Moscow 119333, Russia}

{\small\rm vlasov@ccas.ru}

\end{center}

\bigskip

%The considered Riemann--Hilbert problem appears when moddeling 
%the effect of magnetic field reconnection [1-4]. The statement of
%the problem is as follows. Let domain $G$ on complex plane $z = x + i y$
%be an exteriour of a system of cuts $\Gamma = \Gamma_0 \cup \Gamma^- \cup \Gamma^+$,
%where 
%$\Gamma^+ := \bigl\{z:\, z = R + r\, t\, e^{\,i \pi \alpha},\,\, t \in [0,\, 1]\bigr\}$

The Riemann--Hilbert problem is considered in a decagonal domain $G$ on complex plane,
which is an exteriour of a system $\Gamma$ of cuts $\Gamma_j$ with excluded
infinity. The sought analytic function $\mathcal{F}$ satisfies 
to the boundary condition ${\rm Re} (h\, \mathcal{F}\,) = c$\, on $\Gamma$,
where $h$ and $c$ are prescribed piece--wise constant functions;
$\mathcal{F}$ is continuous in $\overline{G} \setminus \{\infty\}$
and satisfies to a certain growth condition
at infinity. The solution $\mathcal{F}$ has been constructed in analytic form.
Asymptotics for function $\mathcal{F}$ have been found for two limit
cases of geometry of $\Gamma$; first case corresponds to $|\Gamma_j| \to \infty$,
and second case to $|\Gamma_j| \to 0$ for some numbers $j$.
The Riemann--Hilbert problem under consideration originates from magnetic 
hydrodinamics, in model \cite{S06}--\cite{BVS11} of the effect of magnetic field reconnection 
in Solar flares. The model includes a current layer and shock--waves attached to 
its end--points. The constructed solution $\mathcal{F}$ and its 
asymptotics possess clear physical meaning. For construction the asymptotics
we used an approach \cite{VMS89}, \cite{V87} and asymptotics
for Schwarz --- Christoffel integral parameters, that have been found in \cite{BV02}.

This work is supported by the RFBR proj. No. 10-01-00837,
Program No. 3 of the Division of Mathematical Sciences of the RAS
and the ''Contemporary Problems of Theoretical Mathematics`` 
Program of the RAS.

\begin{thebibliography}{6}

\bibitem{S06}
B.V.Somov, \emph{Plasma Astrophysics. Part I.} New York. Springer Science, 2006. 

\bibitem{VMS89}
V.I.Vlasov, S.A.Markovskii, B.V.Somov,
\emph{On an analytical nodel of the magnetic reconnection in plasma} 
Dep. v VINITI Jan. 6, 1989, No. 769-V89 (1989). 

\bibitem{BV02}
S.I.Bezrodnykh, V.I.Vlasov,
\emph{The Riemann--Hilbert problem in a complicated domain 
for the model of magnetic reconnection in plasma}, Comp. Math. Math. Phys.
\textbf{42} 3 (2002), 277--312. 

\bibitem{BVS11}
S.I.Bezrodnykh, V.I.Vlasov, B.V.Somov,
\emph{Generalized analytical models of Syrovatskii's current sheet},
Astronomy Letters. \textbf{37} 2 (2011), 133--150. 

\bibitem{V87}
V.I.Vlasov,
\emph{Boundary value problems in domains with a curvilinear boundary},
Moscow. Vych. Tsentr Akad. Nauk SSSR, 1987. 

\end{thebibliography}

\end{document}
