\documentclass[10pt,a4paper]{article}

%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is at http://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
\usepackage[T2A]{fontenc}
\usepackage[koi8-r]{inputenc}
\usepackage[russian,english]{babel}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\def\p{\partial}
\pagestyle{empty}
\newtheorem{theorem}{Тheorem}

\begin{document}
\begin{center}

%% Title in English:
{\Large Inertial manifolds for strongly damped wave equations}

\bigskip

%% Author 1:
{\sc Natalya Chalkina}

%% Address:
{\small\it Moscow State University, Moscow 119991, Russia}

%% Email:
{\small\rm chalkinan@mail.ru}

\end{center}

\bigskip

%% Abstract in English:

Consider the boundary value problem for a semilinear strongly damped wave equation in a bounded
domain~$\Omega$:
\begin{align}\label{eq_sdwe}
&u_{tt}-2\gamma\Delta u_t=\Delta u+f(u),\quad u\big|_{\partial\Omega}=0,\\
\label{un_sdwe} &u\big|_{t=0}=u_0(x)\in H_0^1(\Omega),\quad u_t\big|_{t=0}=p_0 (x)\in L_2(\Omega).
\end{align}
Here $\gamma>0$ is a coefficient of strong dissipation, and the nonlinearity $f(u)$ satisfies the
global Lipschitz condition:
$$|f(v_1)-f(v_2)|\leqslant L\,|v_1-v_2|\qquad \forall v_1, v_2 \in \R.$$

The following theorem gives sufficient condition for the existence of an inertial manifold for
equation (1).

\begin{theorem}\label{theorem}
Let $\lambda_k$, $0<\lambda_1<\lambda_2\leqslant\dots\to+\infty$, be eigenvalues of the operator
$-\Delta$ in the domain $\Omega$ under the Dirichlet boundary conditions. Suppose that there is an
N such that the following inequalities hold
$$
\lambda_N < \lambda_{N+1} < 
%AC\frac{1}{2\gamma^2}, \eqno(3)
1/(2\gamma^2), \eqno(3)
$$
$$
2L<\sup_{\gamma\lambda_N\leqslant\Phi<\gamma\lambda_{N+1}}\{(\gamma\lambda_{N+1}-\Phi)
\min\{\varkappa_1(\Phi),\varkappa_N(\Phi),\varkappa_{N+1}(\gamma\lambda_{N+1})\}\}, \eqno(4)
$$
where we have used the notation
$$
\varkappa_k (\Phi)=\Phi-\gamma\lambda_k+\sqrt{\Phi^2-2\gamma\lambda_k\Phi+\lambda_k}.
$$
Then, in the phase space $H_0^1(\Omega)\times L_2(\Omega)$, there exists a $2N$-dimensional
inertial manifold that exponentially attracts $($as $t\to+\infty)$ all the solutions of
problem~\textup{(1), (2)}.
\end{theorem}

The proof is based on the construction of a new inner product in the phase space in which gap
property holds and thus an inertial manifold exists (the corresponding general theorem for an
abstract differential equation in a Hilbert space one can find,
e.g., in \cite{gc-2005}).

Remark. If $\gamma$, $\lambda_N$ and $\lambda_{N+1}$ are fixed and they satisfy (3), then we state
the existence of an inetial manifold for sufficiently small $L$.

%\begin{otherlanguage}
%\bigskip
%В теории нелинейных эволюционных уравнений с частными производными большое внимание уделяется
%методам построения инерциальных многообразий, т.е. таких конечномерных липшицевых инвариантных
%многообразий, которые притягивают любые решения этих уравнений при $t\rightarrow +\infty$ с
%экспоненциальной скоростью (см., например, [1]).
%\bigskip
%\end{otherlanguage}

\begin{thebibliography}{p9}

\bibitem{gc-2005}
A.\,Yu. Goritskii and V.\,V. Chepyzhov,
\emph{The Dichotomy Property of Solutions of Quasilinear Equations
in Problems on Inertial Manifolds}, Mat. Sb. \textbf{196} (2005), no. 4, 23--50.

\bibitem{chalkina1}
N.\,A. Chalkina,
\emph{Sufficient Condition for the Existence
of an Inertial Manifold for a Hyperbolic
Equation with Weak and Strong Dissipation},
Russ. J. Math. Phys. \textbf{19} (2012), 11--20.

\end{thebibliography}

\end{document}
