\documentclass[10pt,a4paper]{article}

%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is at http://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
\usepackage[T2A]{fontenc}
\usepackage[koi8-r]{inputenc}
\usepackage[russian,english]{babel}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\pagestyle{empty}

\begin{document}
\begin{center}

%% Title in English:
{\Large Quantum dissipative Zakharov model in a bounded domain}

\bigskip


%% Author 1:
{\sc Igor Chueshov}

%% Address:
{\small\it Kharkov National University, Kharkov 61022, Ukraine}

%% Email:
{\small\rm  chueshov@univer.kharkov.ua}



\end{center}

\bigskip

%% Abstract in English:
We consider an initial boundary value problem for  a
quantum version (introduced in  \cite{GHGO-2005}) of the  Zakharov system
arising in plasma physics:
\begin{equation*}
\left\{\begin{array}{l}
n_{tt}-\Delta\left(n+|E|^2\right)+h^2\Delta^2 n+\alpha n_t  =f(x),
\quad x\in\Omega,\; t>0,
\\ \\
i E_t+\Delta E- h^2\Delta^2E  +i\gamma E - n E=g(x),\quad x\in\Omega,\; t>0.
\end{array}\right.
\end{equation*}
Here $\Omega \subset \R^d$ is a bounded domain, $d\le 3$,
$E(x,t)$ is a complex function
and $n(x,t)$ is a real one, $h>0$,  $\alpha\ge 0$
and $\gamma\ge 0$ are  parameters and $f(x)$, $g(x)$ are given
(real and complex) functions. We also impose some boundary and initial conditions
on $E$ and $n$.
\par
We prove the global well-posedness
of this problem in some Sobolev type classes and study properties of
solutions.  This result confirms the conclusion
recently made in physical literature concerning
the absence of collapse in the quantum Langmuir waves.
(see a discussion in \cite{SSS-2009}). 
In the dissipative case the existence of a
finite dimensional global attractor
is  established and regularity properties
of this attractor are studied. For this we use the recently
developed method of  quasi-stability estimates (see \cite{ChuLas,cl-book}).
In the case when external loads are
$C^\infty$ functions we show that every trajectory  from the attractor
is $C^\infty$ both in time and spatial variables.
This can be interpret as the absence of sharp coherent
structures in the limiting dynamics.  For some details we refer to 
\cite{Chu11}.


\begin{thebibliography}{6}



\bibitem{GHGO-2005}
L. G. Garcia, F. Haas, J. Goedert and L. P. L. Oliveira,
\emph{Modified Zakharov equations for plasmas with a quantum
correction},  Phys. Plasmas {\bf 12} (2005), 012302. 

\bibitem{SSS-2009}
G. Simpson, C. Sulem, and P. L. Sulem,
\emph{Arrest of Langmuir wave collapse by quantum effects},
Phys. Review  {\bf 80} (2009),  056405. 
\bibitem{ChuLas} I.
Chueshov and I. Lasiecka, \textit{Long-Time Behavior of Second Order
Evolution Equations with Nonlinear Damping}, Memoirs of AMS 912, AMS,
Providence, 2008.
\bibitem{cl-book}
I. Chueshov and I. Lasiecka, {\it Von Karman  Evolution Equations},
Sprin\-ger, New York, 2010.  
\bibitem{Chu11}I. Chueshov, \emph{Quantum Zakharov model in a bounded domain},
Preprint   arXiv:1110.1814v1,  9 October 2011.
\end{thebibliography}

\end{document}
