\documentclass[10pt,a4paper]{article}

%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is at http://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
\usepackage[T2A]{fontenc}
\usepackage[koi8-r]{inputenc}
\usepackage[russian,english]{babel}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\pagestyle{empty}

\sloppy


\begin{document}
\begin{center}

%% Title in English:
{\Large Pseudodifferential operator, adiabatic approximation and averaging of linear operators}

\medskip

%% Author 1:
{\sc J. Br\"uning}

{\small\it Humboldt Universit\"at zu Berlin, Berlin 12489, Germany}

{\small\rm bruening@mathematik.hu-berlin.de}

\medskip

{\sc Viktor Grushin}

{\small\it Moscow Institute of Electronics and Mathematics, Moscow 109028, Russia}

{\small\rm vvgrushin@mail.ru}

\medskip

{\sc Sergey Dobrokhotov}

%% Address:
{\small\it Ishlinski Institute for Problems in Mechanics, Moscow 119526, Russia}

%% Email:
{\small\rm dobr@ipmnet.ru}

%% Author 2:


\end{center}

\bigskip

%% Abstract in English:

One use the averaging methods for partial differential equations in the case when their coefficients are rapidly oscillating functions. There exists a great number of publications devoted to averaging, we mention well known monographes by V.Zhikov, S.Kozlov and O.Oleinik, N.Bakhvalov and G.Panasenko, E.Khruslov and V.Marchenko. As a rule averaging methods are used for  construction such asymptotic solutions that their leading term is quite smooth function. From the other hand there exist interesting. The several scale are  in this situation and it  reasonable to use the variant of adiabatic approximation based on the V.Maslov operator methods and pseudodifferential operators. We illustrate this approach using the Sr\"odiger and Klien-Gordon type equations with rapidly oscillating velocity and potential.

This work was supported by RFBR grant 11-01-00973 and DFG-RAS project 436 RUS 113/990/0-1.

\bigskip

%% Abstract in Russian (optional; could be shorter than English):
\begin{otherlanguage}{russian}

\begin{center}
%% Title in Russian (optional):
{\Large  Псевдодифференциальные операторы, адиабатическое приближение и усреднение линейных операторов}
\end{center}

\smallskip

В линейных задачах для уравнений в частных производных методы осреднения работают в ситуациях, когда их коэффициенты- быстро-\break осциллирующие функции. %Имеется огромное количество публикаций, посвященных методам осреднения. мы упомянем  лишь хорошо известные  монографии В.В. Жикова,С.М. Козлова и О.А.Олейник, Н.\,С.~Бахвалова и Г.П.Панасенко, В.А. Марченко и Е.Я. Хруслова, А. Бенсусана, Ж.Лионса, Г. Папаниколау.
Как правило, они применяются для построения таких асимптотических решений исходного уравнения, главный член которых- уже достаточно гладкая  функция. С другой стороны во многих физических задачах интерес представляют ситуации, когда и главный  члена  асимптотического решения- быстроизменяющаяся функция. В этом случае %исходной задаче содержится несколько различных масштабов, и в задаче в 
разумно использовать вариант адиабатического приближения, основанный на операторных методах В.П.Маслова и  псевдодифференциальных операторох. Мы иллюстрируем этот подход на примере  уравнения типа уравнения Шредингера и уравнения Клейна-Гордона (в, частности,  волнового уравнения), с быстроменяющейся скоростью и быстроменяющимся потенциалом.

Работа выполнена  при поддержке гранта РФФИ 11-01-00973 и проекта DFG-РАН 436 RUS 113/990/0-1.

%вида \eqref{C1}
\bigskip

\end{otherlanguage}

%% If you use BIBTEX to create bibliography, please use amsalpha:
%\bibliographystyle{amsalpha}
%\bibliography{physics}%% (if your BIBTEX entries are in physics.bib)
%\end{document}
\end{document}
