\documentclass[10pt,a4paper]{article}

%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is at http://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
\usepackage[T2A]{fontenc}
\usepackage[koi8-r]{inputenc}
\usepackage[russian,english]{babel}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\pagestyle{empty}

\begin{document}
\begin{center}

%% Title in English:
{\Large Statistical Hydrodynamics and Reynolds averaging}

\bigskip

%% Author 1:
{\sc Stamatis Dostoglou}

%% Address:
{\small\it University of Missouri, Columbia, MO 65211, USA}

%% Email:
{\small\rm dostoglous@missouri.edu}


\end{center}

\bigskip

%% Abstract in English:

We shall revisit the Reynolds method of averaging to obtain equations
for turbulent flow in the spirit of M.I. Vishik and A.V. Fursikov's approach to statistical hydrodynamics. In particular, 
for statistically homogeneous flows we shall examine how space averages over domains (as in the original Reynolds ideas) are close to statistical averages on a phase space of vector fields.

We shall also examine Reynolds averages obtained from microscopic statistical mechanics at a hydrodynamic limit via measure disintegration.

\begin{thebibliography}{7}

\bibitem{D1}
Dostoglou, S.
{\em Statistical mechanics for fluid flows.} 
Spectral and Evolution
Problems  vol. {\bf 20}; Proceedings of the 20th Crimean School \& Conference, 193-198, 2010.

\bibitem{D2}
Dostoglou, S.
{\em On Hydrodynamic equations from Hamiltonian dynamics
and 
Reynolds averaging.} Submitted.

\end{thebibliography}

\end{document}
