\documentclass[10pt,a4paper]{article}

%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is at http://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
\usepackage[T2A]{fontenc}
\usepackage[koi8-r]{inputenc}
\usepackage[russian,english]{babel}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\pagestyle{empty}

\begin{document}
\begin{center}

%% Title in English:
{\Large Perturbation theory for systems with multiple stationary regimes}

\bigskip

%% Author 1:
{\sc Mark Freidlin}

%% Address:
{\small\it University of Maryland, College Park, MD 20742, USA}

%% Email:
{\small\rm mif@math.umd.edu}

\end{center}

\bigskip

I 
will 
consider 
deterministic 
and 
stochastic 
perturbations 
of 
dynamical 
systems 
and 
stochastic 
processes 
with 
multiple 
invariant 
measures. 
Long-time 
evolution 
of 
the 
perturbed 
system 
will 
be 
described 
as 
a 
motion 
on 
the 
cone 
of 
the 
invariant 
measures 
of 
the 
non-perturbed 
system. 


Quasilinear 
parabolic 
equations 
with 
a 
small 
parameter 
in 
the 
higher 
derivatives 
\cite{FK10}, 
perturbations 
of 
non-linear 
oscillators 
\cite{FWen12b}, 
\cite{BF00}, 
and 
of 
the 
Landau--Lifshitz 
equation 
for 
magnetization 
\cite{FH12}, 
linear 
elliptic 
PDE's 
with 
a 
small 
parameter 
\cite{FWeb04}, 
\cite{FW12},
\cite{FWen12b}
will 
be 
considered 
as 
examples. 

\begin{thebibliography}{6}
\bibitem{BF00}
M.Brin, M.Freidlin, 
On stochastic behavior of perturbed Hamiltonian systems, 
\emph{Ergodic Theory and Dynamical Systems}, 
\textbf{20} (2000), 
pp. 
55--76.


\bibitem{FH12}
M.Freidlin, W.Hu, 
On perturbations of generalized Landau-Lifshitz dynamics, 
\emph{Journal of Statistical Physics}, 
\textbf{14} (2012), 
5, 
978--1008.


\bibitem{FK10}
M.Freidlin, L.Koralov, 
Nonlinear stochastic perturbations of dynamical systems 
and quasilinear PDE's with a small parameter, 
\emph{Probability Theory and Related Fields}, 
\textbf{147} (2010), 
273--301.


\bibitem{FWeb04}
M.Freidlin, M.Weber, Random perturbations of dynamical 
systems and diffusion processes with conservation laws, 
\emph{Probability Theory and Related Fields}, 
\textbf{128} (2004), 
441--466.


\bibitem{FW12}
M.Freidlin, A.Wentzell, 
\emph{Random Perturbations of Dynamical Systems}, 
Springer, 
2012. 


\bibitem{FWen12b}
M.Freidlin, A.Wentzell,
On the Neumann problem for PDE's with 
a small parameter and the corresponding diffusion processes, 
\emph{Probability Theory and Related Fields}, 
\textbf{152} (2012), 
101--140.

\bibitem{DFK11}
D.Dolgopyat, M.Freidlin, L.Koralov, 
Deterministic and Stochastic perturbations of area preserving 
flows on a two-dimensional torus, 
\emph{Ergodic Theory and Dynamical Systems}
(2011), 
DOI: 10.1017/50143385710000970. 
\end{thebibliography}

\end{document}
