\documentclass[10pt,a4paper]{article}

%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is at http://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
%\usepackage[T2A]{fontenc}
%\usepackage[koi8-r]{inputenc}
%\usepackage[russian,english]{babel}
%\usepackage[english]{babel}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\def\p{\partial}
\pagestyle{empty}

\begin{document}
\begin{center}

%% Title in English:
{\Large Incompressible limit of the linearized Navier--Stokes equations}

\bigskip

%% Author 1:
{\sc Nikolay Gusev}

%% Address:
{\small\it Moscow Institute of Physics and Technology, Dolgoprudny 141700, Russia}

%% Email:
{\small\rm n.a.gusev@gmail.com}

\end{center}

\bigskip

%% Abstract in English:
We consider initial--boundary value problem for linearized equations of viscous
barotropic fluid motion in a bounded domain. We briefly discuss results on
existence, uniqueness and estimates of weak solutions to this problem
(see \cite{IKM,MZ02,G11}).
Then we focus on the asymptotic behaviour of the solutions as the 
compressibility tends to zero, i.e. on the passage to so-called
\emph{incompressible limit} (see \cite{LM98,FN07}).
Briefly, we show that
\begin{itemize}
\item in general case the velocity field converges \emph{weakly} in $L^2(0,T;H_0^1)$;
\item if the initial condition for the velocity is divergence-free
then the velocity converges \emph{strongly} and the pressure
converges $*$-\emph{weakly} in $L^\infty(0,T;L^2)$;
\item if, in addition, the \emph{initial condition} for the pressure
is compatible with the \emph{initial value} of the pressure
in the incompressible problem then the convergence of
the pressure is \emph{strong}. (A similar compatibility condition
was obtained in \cite{Sh99} as a \emph{necessary condition} of strong
convergence of the solutions.)
\end{itemize}
We also demonstrate the necessity of these sufficient conditions using
explicit solutions which are available for simplified data.

\begin{thebibliography}{6}

\bibitem{IKM}
Ikehata R., Koboyashi T. and Matsuyama T.,
Remark on the $L_2$ Estimates of the Density for the Compressible
Navier--Stokes Flow in $R^3$,
Nonlinear Analysis, {\bf 47} (2001), pp. 2519--2526

\bibitem{MZ02}
Mucha P.B. and Zajaczkowski W.M.,
On a $L_p$-estimate for the linearized compressible Navier--Stokes
equations with the Dirichlet boundary conditions,
J. Differential Equations, {\bf 186} (2002), pp. 377--393

\bibitem{G11}
Gusev N.A.,
Asymptotic Properties of Linearized Equations of Low Compressible Fluid Motion,
J. Math. Fluid Mech. (2011), DOI: 10.1007/s00021-011-0084-8

\bibitem{LM98}
{Lions P.-L. and Masmoudi N.},
Incompressible limit for a viscous compressible fluid,
J. Math. Pures Appl., {\bf 77(6)} (1998), pp. 585--627

\bibitem{FN07}
Feireisl E. and Novotn\'{y} A.,
The Low Mach Number Limit for the Full Navier--Stokes--Fourier
System,
Arch. Rational Mech. Anal., {\bf 186} (2007), pp. 77--107

\bibitem{Sh99}
Shifrin E.G.,
Unsteady Flows of Viscous Slightly Compressible Fluids: the
Condition of Continuous Dependence on Compressibility,
Doklady Physics, {\bf 44}, No. 3 (1999), pp. 189--192


\end{thebibliography}

\end{document}
