\documentclass[10pt,a4paper]{article}

%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is athttp://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
%\usepackage[T2A]{fontenc}
%\usepackage[koi8-r]{inputenc}
%\usepackage[russian,english]{babel}
%\usepackage[english]{babel}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\def\p{\partial}
\pagestyle{empty}

\begin{document}
\begin{center}

%% Title in English:

{\Large Bony and thick attractors}
%\footnote{
%The research was supported by
%part by the grants NSF 0700973, RFBR 10-01-00739-à, RFFI-CNRS
%10-01-93115-NTSNIL-a.}
%}

\bigskip

%% Author 1:
{\sc Yu.~S.~Ilyashenko}

%% Address:
{\small\it Moscow State and Independent Universities, Steklov Mathematics Institute,  National Research University Higher School of Economics, Cornell University}%MULTIPLE

%% Email:
{\small\rm yulijs@gmail.com}

\end{center}

\smallskip

Understanding of the structure of attractors of generic dynamical systems
is one of the major goals of the theory.
%%AC of these systems.
A vast general
program suggested by Palis  presents numerous conjectures
about this structure. Various particular cases of these conjectures are proved
in numerous papers that we do not quote here.
Main part of these investigations is related to diffeomorphisms  of closed manifolds.
Our investigation is
%%AC in a sense
parallel to this direction of research. In the first part of the talk,
attractors of  \emph{manifolds with boundary onto themselves} are studied. At present, locally generic
properties of  attractors of such maps are established, that are not yet observed
(and plausibly do not hold)  for the case of closed manifolds.
For instance, an open set of diffeomorphisms  of manifolds with boundary onto themselves
may have attractors with intermingled basins.
The strongest result of this kind
is
% obtained
% by Kleptsyn and Saltykov
in
\cite{KS}.

Another property of this kind is \emph{having thick attractors}.
It is a general belief that attractors of typical smooth dynamical systems
(diffeomorphisms and flows) on closed manifolds
either coincide with the whole phase space
or have Lebesgue measure zero. In this talk we show that this is not the fact
for diffeomorphisms  of manifolds with boundary onto themselves. Namely, in the space of diffeomorphisms  of
%a product 
$T^2  \times [0,1]$, there exists an open set such that  any map from a complement of this set
to a countable number of hypersurfaces,  has a
thick attractor: a transitive attractor that has positive Lebesgue measure together with its complement \cite{I11}.
The problem whether
%or not
thick
attractors exist for locally generic diffeomorphisms
of a closed manifold remains  widely open.

In the second part we study so called bony attractors. These are attractors of
skew products over a Bernoulli shift with the following unexpected property:
the map has an invariant manifold, and the intersection of the attractor with
that manifold, called \emph{a bone}, is much larger than the attractor of the restriction of the map
to the invariant manifold.  Bony attractors with one-dimensional bones
were discovered in \cite{K10}.
We construct bones of arbitrary dimension \cite{I12}.
It is expected that bony attractors are in a sense locally generic.
% in the space of diffeomorphisms  of a closed manifold.
\vskip -0.6cm \ 

\begin{thebibliography}{7}

\bibitem{I11} Yu. Ilyashenko,
\emph{Thick attractors of boundary preserving diffeomorphisms},
Indagationes Mathematicae
\textbf{22} (2011), no. 3-4, 257--314.

\bibitem{I12} Yu. Ilyashenko,
\emph{Multidimensional bony attractors}, accepted to  Functional
Analysis and applications (Russian).

\bibitem{KS} V. Kleptsyn, P. Saltykov,
\emph{On $ C^2$-robust atractors with intermingled basins
for boundary preserving maps}, Proceedings of
% the 
MMS \textbf{72} (2011),
% no. 2,
249--280.

\bibitem{K10}
Yu.\,G\,Kudryashov, \emph{Bony attractors},
Func. Anal. Appl. \textbf{44} (2010),
no. 3, 
73--76.


\end{thebibliography}

\end{document}
