\documentclass[10pt,a4paper]{article}

%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is at http://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
\usepackage[T2A]{fontenc}
\usepackage[koi8-r]{inputenc}
\usepackage[russian,english]{babel}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\def\p{\partial}
\pagestyle{empty}

\begin{document}
\begin{center}

%% Title in English:
{\Large Symplectic projection methods of deriving long-time asymptotics for nonlinear PDEs}

\bigskip

%% Author 1:
{\sc Valeriy Imaykin}

%% Address:
{\small\it Research Institute of Innovative Strategies for General Education Development, Moscow 109544, Russia}
%%{\small\it Research Institute of Innovative Strategies for General Education Development, Mezhdunarodnaya str. 11, Moscow 109544, Russia}

%% Email:
{\small\rm ivm61@mail.ru}


\bigskip

%% Author 2:
\end{center}

\bigskip

%% Abstract in English:
We consider some systems which describe a field-particle interaction, namely a charged particle coupled to the scalar wave field, to the Klein-Gordon field, and to the Maxwell field. Since the systems are Hamiltonian, methods of symplectic projection onto invariant finite-dimensional manifolds of soliton-type solutions turn to be helpful in deriving long-time asymptotics of solutions, \cite{IKV05,IKV06,IKS11,IKV11}.

%\begin{otherlanguage}{russian}

%\bigskip

%\begin{center}
%% Title in Russian (optional):
%{\Large История уравнения Клейна-Гордона}
%\end{center}

%\smallskip

%% Abstract in Russian (optional; could be shorter than English):
%\end{otherlanguage}

%% If you use BIBTEX to create bibliography, please use amsalpha:
%\bibliographystyle{amsalpha}
%\bibliography{physics}%% (if your BIBTEX entries are in physics.bib)
%\end{document}

\begin{thebibliography}{4}

\bibitem{IKV05} V.~Imaikin, A.~Komech, and B.~Vainberg,
\emph{On scattering of solitons for the Klein-Gordon equation coupled to a particle}, 
Comm. Math. Phys. \textbf{268} (2006), 321--367.

\bibitem{IKV06} V.~Imaikin, A.~Komech, and B.~Vainberg,
\emph{On scattering of solitons for wave equation coupled to a particle}, in ``CRM
Proceedings and Lecture Notes'', \textbf{42} (2007).

\bibitem{IKS11} V.~Imaikin, A.~Komech, and H.~Spohn, \emph{Scattering asymptotics for a charged particle coupled to the Maxwell field}, J. Math. Phys. \textbf{52}, (2011).

\bibitem{IKV11} V.~Imaikin, A.~Komech, and B.~Vainberg, \emph{Scattering of Solitons for Coupled
Wave-Particle Equations}, accepted in J. Math. Anal. Appl. (2011).

\end{thebibliography}

\end{document}
