\documentclass[10pt,a4paper]{article}

%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is at http://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
\usepackage[T2A]{fontenc}
\usepackage[koi8-r]{inputenc}
\usepackage[russian,english]{babel}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\def\p{\partial}
\pagestyle{empty}

\begin{document}
\begin{center}

%% Title in English:
{\Large On global attractors  of  nonlinear hyperbolic PDEs}

\bigskip

%% Author 1:
{\sc Alexander Komech}

%% Address:
{\small\it IITP, Moscow, Russia and Vienna University}

%% Email:
{\small\rm akomech@iitp.ru}


\end{center}

\bigskip

%% Abstract in English:

We consider Klein-Gordon and Dirac equations
coupled to U(1)-invariant nonlinear
oscillators. Solitary waves of the coupled nonlinear system form
two-dimensional submanifold in the Hilbert phase space of finite
energy solutions. 
\medskip

\noindent
{\bf Main Theorem.}
Let all the oscillators be  strictly nonlinear.
Then  any finite energy solution converges,
in the long time limit,
to the solitary manifold
in the local energy seminorms.

\medskip

The investigation is inspired by Bohr's postulates on transitions to
quantum stationary states.
The results are obtained for:

\medskip

\noindent
$\bullet$
1D KGE coupled to one oscillator [1,2,3], and to finitely many
oscillators [4];

\medskip

\noindent
$\bullet$
$n$D KGE  and Dirac coupled to one oscillator via mean field
interaction [5,~6].

\bigskip

\noindent
[1] A.I. Komech, On attractor of a singular nonlinear
$U(1)$- invariant Klein-Gordon equation, p. 599-611 in: Proc.
$3^{rd}$ ISAAC Congress,  Berlin, 2003.

\smallskip
\noindent
[2] A.I. Komech, A.A. Komech,
On global attraction to solitary waves for the
Klein-Gordon equation coupled to nonlinear oscillator,
{\em C. R., Math., Acad. Sci. Paris} {\bf 343},  111-114.

\smallskip
\noindent
[3] A.I. Komech, A.A. Komech,
Global attractor for a nonlinear oscillator coupled
to the Klein-Gordon field,
{\em Arch. Rat. Mech. Anal.} {\bf 185} (2007), 105-142.

\smallskip
\noindent
[4] A.I. Komech, A.A. Komech, On global attraction to solitary
waves for the Klein-Gordon field coupled to several nonlinear
oscillators, {\em J. Math. Pures Appl.},
{\bf 93} (2010), 91-111. 

\smallskip
\noindent
[5] A.I. Komech, A.A. Komech, Global attraction to solitary waves
for Klein-Gordon equation with mean field interaction, {\em Annales
de l'IHP-ANL} {\bf 26} (2009), no. 3,  855-868.
arXiv:math-ph/0711.1131

\smallskip
\noindent
[6] A.I. Komech, A.A. Komech, Global attraction to solitary waves
for nonlinear Dirac equation with mean field interaction, 
{\em SIAM J. Math. Analysis} {\bf 42} (2010), no.6, 2944-2964.

\end{document}
