\documentclass[10pt,a4paper]{article}
\nonstopmode
%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is at http://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
\usepackage[T2A]{fontenc}
\usepackage[koi8-r]{inputenc}
\usepackage[russian,english]{babel}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\pagestyle{empty}

\begin{document}
\begin{center}

%% Title in English:
{\Large Weak attractor for the Klein-Gordon equation with a nonlinear oscillator in discrete space-time}

\bigskip


\bigskip

%% Author 1:
{\sc Andrey Komech}

%% Address:
{\small\it IITP, Moscow, Russia}
{\small\it and}
{\small\it Texas A\&M University, College Station, TX, USA}

%% Email:
{\small\rm andrey.komech@gmail.com}

\end{center}

\bigskip

%% Abstract in English:

We consider the Klein-Gordon equation
in the discrete space-time
interacting with a nonlinear oscillator.
In \cite{kg-discrete-arxiv},
we prove that the weak attractor of all
finite energy solutions
coincides with the set of all
multifrequency solitary waves,
\[
\sum\sb{j=1}\sp{N}\phi\sb j(x)e^{-i\omega\sb j t},
\qquad
(x,\,t)\in\Z^n\times\Z,
\quad
\phi\sb j\in l\sp 2(\Z^n),
\quad
\omega\sb j\in\R\mod 2\pi.
\]
More precisely, we show that
there are only one-, two-, and four-frequency solitary waves.
In the continuous limit,
only the one-frequency solitary waves survive.
The convergence to the attractor takes place weakly
(on finite subsets or in the weighted norms).
The proof is based on a version
of the Titchmarsh convolution
theorem proved for distributions
supported on a circle \cite{titchmarsh-circle}.

The result generalizes an earlier
result for the Klein-Gordon equation
in the continuous space-time \cite{ubk-arma}.

%\bibliographystyle{amsplain}
%\bibliography{comech}
%\end{document}

\begin{thebibliography}{6}

\bibitem{kg-discrete-arxiv}
Andrew Comech, \emph{Weak attractor of the {K}lein-{G}ordon field in discrete
  space-time interacting with a nonlinear oscillator}, ArXiv e-prints
  \textbf{1203.3233} (2012).

\bibitem{ubk-arma}
Alexander~I. Komech and Andrew~A. Komech, \emph{Global attractor for a
  nonlinear oscillator coupled to the {K}lein-{G}ordon field}, Arch. Ration.
  Mech. Anal. \textbf{185} (2007), 105--142.

\bibitem{titchmarsh-circle}
Alexander~I. Komech and Andrew~A. Komech, \emph{On the {T}itchmarsh convolution theorem for distributions on a
  circle}, Funktsional. Anal. i Prilozhen. \textbf{46} (2012), to appear (see
  arXiv:1108.2463).

\end{thebibliography}

\end{document}
