\documentclass[10pt,a4paper]{article}

%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is at http://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
%\usepackage[T2A]{fontenc}
%\usepackage[koi8-r]{inputenc}
%\usepackage[russian,english]{babel}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\pagestyle{empty}

\begin{document}
\begin{center}

%% Title in English:
{\Large Dispersive estimates for magnetic Klein-Gordon equation}

\bigskip



%% Author 1:
{\sc Elena Kopylova}

%% Address:
{\small\it Institute for Information Transmission Problems, Moscow 127994, Russia}

%% Email:
{\small\rm ek@iitp.ru}

\end{center}

\bigskip

%% Abstract in English:

We obtain a dispersive long-time decay in weighted
energy norms for solutions of  3D Klein-Gordon equation
with magnetic and scalar potentials.
The decay extends the results of \cite{kopylovaJK}, 
\cite{kopylovaK} and \cite{kopylovaKK} for the  Schr\"odinger, wave 
and Klein-Gordon equations  with  scalar potentials.
For the proof we develop the spectral
theory of Agmon, Jensen and Kato and minimal escape velocities 
estimates of  Hunziker, Sigal and Soffer.

\begin{thebibliography}{}

\bibitem{kopylovaA}
S. Agmon, \emph{Spectral properties of Schr\"odinger operator 
and scattering theory},
Ann. Scuola Norm. Sup. Pisa, Ser. IV, \textbf{2} (1975), 151--218.

\bibitem{kopylovaHSS}
W. Hunziker, I.M. Sigal, A. Soffer,
\emph{Minimal escape velocities},
Comm. Partial Diff. Eqs., \textbf{24} (1999), no. 11-12, 2279--2295.

\bibitem{kopylovaJK}
A. Jensen, T. Kato,
\emph{Spectral properties of Schr\"odinger operators and time-decay
of the wave functions}, 
Duke Math. J., \textbf{46} (1979), 583--611.

\bibitem{kopylovaKK}
A. Komech, E. Kopylova, 
\emph{Weighted energy decay for 3D Klein-Gordon equation},
J. Diff. Eqs., \textbf{248} (2010), no. 3, 501--520.

\bibitem{kopylovaK}
E. Kopylova,
\emph{Weighed energy decay for 3D wave equation}, 
Asymptotic Anal., \textbf{65} (2009), no. 1-2, 1--16.

\end{thebibliography}

\end{document}
