% !Mode:: "TeX:UNIX:CP1251"
\documentclass[10pt,a4paper]{article}

%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is at http://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
\usepackage[T2A]{fontenc}
\usepackage[koi8-r]{inputenc}
\usepackage[russian,english]{babel}
\usepackage{url}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\def\p{\partial}
\pagestyle{empty}

\begin{document}
\begin{center}

%% Title in English:
{\Large Disprove of the commonly recognized belief that the foreign exchange currency market is self-stabilizing}

\bigskip

%% Author 1:
{\sc Victor Kozyakin}

%% Address:
{\small\it Institute for Information Transmission Problems, Moscow, Russia}

%% Email:
{\small\rm kozyakin@iitp.ru}

\end{center}

\bigskip

%% Abstract in English:
In economics and finance, arbitrage is the practice of taking
advantage of a price difference between two or more markets. The
act of exploiting an arbitrage opportunity resulting from a pricing
discrepancy among three different currencies in the foreign
exchange market is called triangular arbitrage (also referred to as
cross currency arbitrage or three-point arbitrage). The commonly
recognized belief in economics and finance is that
\begin{quote}
\ldots Arbitrage has the effect of causing prices in different
markets to converge. As a result of arbitrage, the currency
exchange rates, the price of commodities, and the price of
securities in different markets tend to converge\ldots
\end{quote}
see, e.g. \url{http://en.wikipedia.org/wiki/Arbitrage}.

In the talk, the triangle arbitrage operations will be reformulated
in terms of the so-called asynchronous systems. This will allow to
disprove the above belief by a set of examples. It will be
demonstrated that the foreign exchange currency market may exhibit
periodical regimes and exponential growth of exchange rates but
also unexpectedly strong instability: the so-called
double-exponential growth of exchange rates.

\bigskip

\begin{otherlanguage}{russian}

\begin{center}
{\Large Опровержение общепринятого в финансовой экономике постулата о самостабилизации валютного рынка}
\end{center}

\smallskip

В финансовой экономике под арбитражем понимается практика получения
выгоды за счет разницы цен между двумя или более рынками. В том
случае, когда выгода получается за счет несоответствия цен между
тремя участниками валютного рынка, арбитраж называется треугольным
(а также межвалютным, трехточечным или, в русской литературе, ---
пространственным). В финансовой экономике общепринят постулат о
том, что
\begin{quote}
\ldots Арбитраж приводит к стабилизации (сходимости) цен на
различных рынках. Как результат, обменные курсы валют, цены товаров
и стоимости ценных бумаг на различных рынках стабилизируются
(сходятся)\ldots
\end{quote}
см., например, \url{http://en.wikipedia.org/wiki/Arbitrage}.

В докладе будет предложено описание арбитражных операций в терминах
так называемых асинхронных или рассинхронизованных систем. Такой
подход позволит опровергнуть вышеупомянутый постулат с помощью
серии примеров. В частности, будет показано, что в динамике
валютного рынка могут иметь место периодические режимы,
экспоненциальный рост курсов обмена валют, а также неожиданно
сильная неустойчивость динамики в виде режимов, имеющих так
называемую сверхэкспоненциальную скорость роста.

\bigskip
\end{otherlanguage}
\end{document}
