\documentclass[10pt,a4paper]{article}

%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is at http://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
\usepackage[T2A]{fontenc}
\usepackage[koi8-r]{inputenc}
\usepackage[russian,english]{babel}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\def\p{\partial}
\pagestyle{empty}

\begin{document}
\begin{center}

%% Title in English:
{\Large The structure of the solution sets for generic operator equations}

\bigskip

%% Author 1:
{\sc Alexander Krasnosel'skii}

%% Address:
{\small\it Institute for Information Transmission Problems, Moscow, Russia}

%% Email:
{\small\rm amk@iitp.ru}

\end{center}

\bigskip

%% Abstract in English:
Consider an abstract operator equation  $x=F(x,\lambda)$ in a Banach space $X$
(all constructions are interesting even in $\R^{2}$) with
compact and continuous operator $F$ depending on a parameter $\lambda\in\Lambda$.
Here $\Lambda$ is a compact set, say an interval or the circle $S^{1}$.
The set of all solutions of the equation  $x=F(x,\lambda)$ in the space
$X\times\Lambda$ may have very complicated form (e.g. may have a fractal structure).
However, these sets have some common properties,
for example such sets are always compact.
Under generic topological assumptions (partially, if $F$ satisfies the Schauder principle conditions:
it maps some ball in its interior part) such equations
always have large connected components.
The first results in this direction were obtained by Mark Krasnosel'skii
in 50's, later his ideas were continued and developed by various authors.

In my talk I would like to present some new results
on the structure of the solution sets for generic operator equations.
Possible applications to boundary value problems are evident,
as an example I present some statements on nontrivial asymptotic bifurcation
points in the problems on periodic forced oscillations
for higher order ODE.
In these statements the set of all solutions
in the space $X\times\Lambda$ is nonconnected and consists
from the infinite sequence of bounded cyclic branches
going to infinity.

\bigskip

%% Abstract in Russian (optional; could be shorter than English):

\begin{otherlanguage}{russian}

\begin{center}
%% Title in Russian (optional):
{\Large О структуре множеств решений операторных уравнений общего вида}
\end{center}

\smallskip

Рассмотрим абстрактное операторное уравнение $x=F(x,\lambda)$ в банаховом пространстве $X$
(все построения интересны уже в $\R^{2}$) с вполне непрерывным по совокупности
переменных оператором $F$, зависящим от параметра $\lambda\in\Lambda$.
Здесь $\Lambda$ --- некоторый компакт, например отрезок или окружность.
Множество решений такого уравнения в пространстве $X\times\Lambda$ может быть
устроено очень сложно (при отсутствии гладкости). Однако, некоторые общие свойства у таких множеств
имеются, например компактность. В естественных топологических предположениях
(в частности, при выполнении условий принципа Шаудера: если $F$ преобразует
шар в свою внутренность)
у таких уравнений существуют большие связные компоненты. Первые результаты в
этом направлении были получены в 50х годах прошлого века Марком Красносельским,
далее идеи продолжали и развивали различные авторы, в основном для конкретных
приложений общей теории.

В докладе будут рассказаны новые утверждения о структуре
множеств решений операторных уравнений. Возможные приложения к
краевым задачам очевидны, в качестве примера
будут предложены утверждения об нетривиальных
асимптотических точках бифуркации в задаче о вынужденных
колебаниях для дифференциальных уравнений старшего порядка.
Будут сформулированы условия существования в пространстве
$X\times\Lambda$ несвязных неограниченных структур решений,
имеющих
форму последовательностей ограниченных циклических ветвей,
уходящих на бесконечность.

\bigskip

\end{otherlanguage}


\end{document}
