\documentclass[10pt,a4paper]{article}

%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is at http://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
\usepackage[T2A]{fontenc}
\usepackage[koi8-r]{inputenc}
\usepackage[russian,english]{babel}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\pagestyle{empty}

\begin{document}
\begin{center}

%% Title in English:
{\Large The trajectory attractor of the nonlinear hyperbolic equation, contain a small parameter by the second derivative with respect to time}

\bigskip

%% Author 1:
{\sc Andrey Lyapin}

%% Address:
{\small\it Russian State Technological University (MATI)}

%%Email:
{\small\rm andser2001@gmail.com}

\end{center}

\bigskip

%% Abstract in English:

In many articles dealt with the convergence of the attractor of the nonlinear autonomous hyperbolic equation, contain a small parameter by the second derivative with respect to time, to the attractor of the limit ($\varepsilon = 0$) parabolic equation (for example: [1], [2], [3]). It was assumed that the Cauchy problem for the limit of the parabolic equation has a unique solution. In the present report focuses on the case when there is no uniqueness of solutions of the Cauchy problem for these equations. It is shown that the trajectory attractor of a hyperbolic equation converges to the trajectory attractor of the limit parabolic equation in an appropriate topology. 

\bigskip

%% Abstract in Russian (optional; could be shorter than English):

\begin{otherlanguage}{russian}

\begin{center}
%% Title in Russian (optional):
{\Large Траекторный аттрактор нелинейного гиперболического уравнения с малым параметром при старшей производной по времени.}
\end{center}

\smallskip

В ряде работ (смотри, например, [1], [2] и [3]) изучался вопрос о сходимости аттрактора нелинейного автономного гиперболического уравнения, содержащего малый параметр при второй производной по времени, к аттрактору предельного (при $\varepsilon = 0$) параболического уравнения. При этом предполагалось, что задача Коши для предельного параболического уравнения имеет единственное решение. В настоящей работе основное внимание уделяется тому случаю, когда не имеет место единственность решения задачи Коши для этих уравнений. В работе показано, что траекторный аттрактор гиперболического уравнения сходится к траекторному аттрактору предельного параболического уравнения в соответствующей топологии.

\bigskip

\end{otherlanguage}



\noindent [1]
V.V. Chepyzhov, M.I. Vishik, Perturbation of trajectory attractors for dissipative hyperbolic equations. \textit{Op. Theory: Adv. Appl. } \textbf{110} (1999), 33--54.
\vspace{2ex}

\noindent [2]
V.V. Chepyzhov, M.I. Vishik, \textit{Attractors for equations of mathematical physics} Amer. Math. Soc., Colloquium publications vol. \textbf{49} (2002).
\vspace{2ex}

\noindent [3]
A. Haraux,
\emph{Two remarks on dissipative hyperbolic problems}. Nonlinear partial differential equations and their applications, \textit{College de France Seminar} \textbf{7} (1985), 161--179.
\vspace{2ex}

\noindent [4]
Hale, G.Raugel. Upper semicontinuity of the attractors for singular perturbed
hyperbolic equation, \textit{J. Diff. Eq.} \textbf{73} (1988), 197--214.
\vspace{2ex}

\noindent [5]
S.V. Zelik. Asymptotic regularity of solutions of singularly perturbed damped wave equations 
with supercritical nonlinearities, \textit{Discrete Contin. Dyn. Syst.} \textbf{11} (2004), 351--392.


\end{document}
