\documentclass[10pt,a4paper]{article}

%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is at http://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
\usepackage[T2A]{fontenc}
\usepackage[koi8-r]{inputenc}
\usepackage[russian,english]{babel}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\def\p{\partial}
\pagestyle{empty}

\begin{document}
\begin{center}

%% Title in English:
{\Large Structure of the minimum-time damping of a physical pendulum}

\bigskip

%% Author 1:
{\sc Alexander Ovseevich}

%% Address:
{\small\it Institute for Problems in Mechanics, Moscow 1119526, Russia}

%% Email:
{\small\rm ovseev@ipmnet.ru}

\end{center}

\bigskip

%% Abstract in English:
We study the  minimum-time damping of a physical pendulum by means of a
bounded control. In the similar problem for a linear oscillator each optimal trajectory possesses a
finite number of control switchings from  the maximal to the minimal value. If one considers
simultaneously all optimal trajectories with any initial state, the number of switchings can be
arbitrary large. We show that for the nonlinear pendulum there is a uniform bound for the switching
number for all optimal trajectories. We find asymptotics for this bound as the control amplitude
goes to zero.

\begin{otherlanguage}{russian}

\bigskip

\begin{center}
%% Title in Russian (optional):
{\Large Структура оптимального  быстродействия для физического маятника}
\end{center}

\smallskip

%% Abstract in Russian (optional; could be shorter than English):
Рассматривается задача  быстрейшего приведения физического маятника в состояние устойчивого
равновесия с помощью ограниченного управления. В аналогичной задаче для линейного маятника на каждой
оптимальной траектории имеется конечное число переключений управления с максимального на минимальное
значение, если же рассматривать все оптимальные траектории с произвольным начальным состоянием, то
соответствующее количество переключений может быть сколь угодно велико. Мы показываем, что для
нелинейного маятника имеется общая верхняя граница для количества переключений на всех оптимальных
траекториях.  Найдена асмптотика этого числа в ситуации, когда возможности управления малы.

\bigskip
\end{otherlanguage}

\begin{thebibliography}{7}

\bibitem{pont} {L.S. Pontryagin, V.G. Boltyanskii, and R. Gamkrelidze,}
{\em Matematicheskaya teoriya optimalnykh protsessov},
Nauka, Moscow, 1983.


\bibitem{resh} {S.A. Reshmin},
\emph{Bifurcation in the time-optimality problem for a second-order nonlinear system},
Prikl. Mat. Mekh. \textbf{73} (2009), 562--572.

\bibitem{flag} {\em Garcia Almuzara J.L., Fl\"ugge-Lots I.} Minimum time control of a nonlinear system. {\em J.
Differential Equations.} 1968. Vol. 4, no. 1, pp. 12--39.


\bibitem{akulenko}{Leonid Akulenko},
\emph{Problems and methods of optimal control}, Nauka, Moscow, 1987; Kluwer, Dordrecht, 1994.

\bibitem{akulenko2}{F.L. Chernousko, L.D. Akulenko, and B.N. Sokolov},
\emph{Upravlenie kolebaniyami.} Nauka, Moscow, 1980.
\end{thebibliography}

\end{document}
