\documentclass[10pt]{article}
%\usepackage[russian]{babel}
\usepackage{amsfonts,amsmath,amssymb}
%\usepackage[dvips]{graphicx}

%% Enabling Cyrillic input with koi8-r encoding:
\usepackage[T2A]{fontenc}
\usepackage[koi8-r]{inputenc}
\usepackage[russian,english]{babel}



%\sloppy \textwidth18cm \textheight25cm \hoffset-2.5cm \voffset-3cm
%\parindent0cm
%\parskip2.5mm
%\unitlength1cm

\def\p{{\partial}}

\def\va{{\varphi}}
\def\c{{\mbox{\bf c}}}

\def\cT{{\cal T}}
\def\ot{{\overline{\theta}}}
\def\oA{{\overline{A}}}
\def\od{{\stackrel{\rm def} {=} }}
\def\bS{{\bf S}}
\def\Go{\Gamma(0)}
\def\Ooj{\Omega_{0j}}
\def\uj{^{j}}
\def\dd{\partial}
\def\Tr{{\bf Tr}}
\def\zrho{\varrho_0}
\def\ut{^{2}}
\def\uo{^{1}}
\def\hWj{\widehat{W}^{j}}
\def\hFj{\widehat{F}^{j}}
\def\dhrho{\delta\widehat{\varrho}}
\def\hpsi{\widehat{\psi}}
\def\uk{^\kappa}
\def\tK{\tilde{K}}
\def\tpsi{\tilde{\psi}}
\def\J{{\cal J}}
\def\S{{\cal S}}


\pagestyle{empty}


\begin{document}

\begin{center}
{\Large On global solutions to the Cauchy problem for discrete kinetic equations}

\bigskip

%% Author 1:
{\sc Evreny Radkevich}

%% Address:
{\small\it Moscow State University, Moscow 119991, Russia}

%% Email:
{\small\rm evrad07@gmail.com}
\end{center}

\bigskip

The kinetic theory considers the gas as a collection of a huge number of randomly moving particles, in some way interacting with each other.
As a result of these interactions the particles exchange momenta and energies.
Interaction can be through direct collisions or by certain forces.
To elucidate the mathematical scheme describing such phenomena,
we consider \cite{radkevich1} the so-called discrete kinetic Boltsmann equations
and give a phenomenological derivation of the Boltsmann equation
for the model of gas with finitely many particle velocities
and finitely many different interactions
(Broadwell-type model \cite{radkevich2}):
\[
\p_tn_j+(\omega_{ix}\p_x+\omega_{iy}\p_y+\omega_{iz}\p_z)
n_j=\sum_{k,l,j; k\ne i, l\ne i, j\ne  i}\sigma^{ij}_{kl}(n_kn_l-n_in_j),
~~1\le i\le N.
\]
For the discrete kinetic equations \cite{radkevich3}
(in dimensions $d=1,2,3$)
we prove the existence of a global solution, its decomposition with respect to smoothness,
and consider the influence of oscillations born by the interaction operator.

\begin{otherlanguage}{russian}

\bigskip

\begin{center}
%% Title in Russian (optional):
{\Large О глобальных решениях задачи Коши для дискретных кинетических уравнений}
\end{center}

\smallskip

%% Abstract in Russian (optional; could be shorter than English):
Кинетическая теория рассматривает газ как совокупность громадного числа хаотически движущихся частиц тем или иным образом взаимодействующих между собой. В результате таких взаимодействий частицы обмениваются импульсами, энергией. Взаимодействие может осуществляться путем прямого столкновения частиц или при помощи тех или иных сил. Для пояснения математической схемы, описывающей подобные явления, в \cite{radkevich1} рассматриваются так называемые дискретные модели кинетического уравнения Больцмана и приводится феноменологический вывод уравнения Больцмана для газовой модели с конечным числом различных скоростей частиц и конечным числом разных взаимодействий (модели типа Бродуэлла \cite{radkevich2})
\[
\p_tn_j+(\omega_{ix}\p_x+\omega_{iy}\p_y+\omega_{iz}\p_z)
n_j=\sum_{k,l,j; k\ne i, l\ne i, j\ne  i}\sigma^{ij}_{kl}(n_kn_l-n_in_j),
~~1\le i\le N.
\]
Для дискретных уравнений кинетики \cite{radkevich3}
(размерности $d=1,2,3$) доказано существование глобального решения, получено разложение его по гладкости, исследовано влияние осцилляций, порождаемых оператором взаимодействия.

\bigskip

\end{otherlanguage}

\begin{thebibliography}{6}
\bibitem[1]{radkevich1}
S.K.\,Godunov and U.M.\,Sultangazin,
\emph{Discrete models of the {B}oltzmann kinetic equation},
Uspehi Mat. Nauk,
{\bf 26} (1971), 3--51.


\bibitem[2]{radkevich2}
J.E.~Broadwell,
\emph{Study of rarefied shear flow by the discrete velocity method},
J. Fluid Mech. {\bf 19} (1964), 401--414.

\bibitem[3]{radkevich3}
E. Radkevich,
\emph{On existence of global solutions
to the Cauchy problem
for discrete kinetic equations},
Journal of Mathematical Sciences {\bf 181} (2012), 232--280.
\end{thebibliography}

\end{document}
