\documentclass[10pt,a4paper]{article}

%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is at http://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
\usepackage[T2A]{fontenc}
\usepackage[koi8-r]{inputenc}
\usepackage[russian,english]{babel}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\pagestyle{empty}

\begin{document}
\begin{center}

%% Title in English:
{\Large Branching random motions, nonlinear hyperbolic systems and traveling waves}

\bigskip

%% Author 1:
{\sc Nikita Ratanov}

%% Address:
{\small\it Universidad del Rosario, Bogot\'a, Colombia}

%% Email:
{\small\rm nratanov@urosario.edu.co}

\end{center}

\bigskip
It is known that under certain assumptions for nonlinearities the 
following coupled nonlinear hyperbolic equations
\[
\left\{
\begin{aligned}
\frac{\partial u_+}{\partial t}-c\frac{\partial u_+}{\partial x}
=&\mu_+(u_--u_+)-\lambda_+u_++F_+(u_+, u_-),\\
\frac{\partial u_-}{\partial t}+c\frac{\partial u_-}{\partial x}
=&\mu_-(u_+-u_-)-\lambda_-u_-+\lambda_-F_-(u_+, u_-),
\end{aligned}
\right.
\]
have traveling-wave solutions. 

We realize the McKean's program \cite{McK323} for the 
Kolmogorov-Petrovskii-Piskunov equation in this hyperbolic case. 
%The Feynman-Kac formula based on branching telegraph processes plays a key role.

%% Abstract in English:
A branching random motion on a line, 
with abrupt changes of direction, is studied. 
The
branching mechanism, 
being independent of random motion, and intensities of reverses are defined
by a particle's current direction. 
A solution of a certain hyperbolic system of coupled non-linear
equations (Kolmogorov type backward equation)
have a so-called McKean representation via such
processes. Commonly this system possesses travelling-wave solutions. 
The convergence of solutions
with Heaviside terminal data to the travelling waves is discussed.

The Feynman-Kac formula plays a key role, \cite{ratanov}.

\begin{thebibliography}{6}

\bibitem{McK323}
H.P. McKean,  \emph{Application of Brownian motion to the equation of Kolmogorov-Petrovskii-Piskunov}, Comm. Pure Appl. Math.
XXVIII (1975), 323-331.

\bibitem{ratanov}
N. Ratanov, \emph{Branching random motion,
nonlinear hyperbolic systems and travelling waves}, ESAIM: Probability and Statistics, 
{\bf{10}} (2006),  236-257

\end{thebibliography}

\end{document}
