\documentclass[10pt,a4paper]{article}

%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is at http://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
\usepackage[T2A]{fontenc}
\usepackage[koi8-r]{inputenc}
\usepackage[russian,english]{babel}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\def\p{\partial}
\pagestyle{empty}

\begin{document}
\begin{center}

%% Title in English:
{\Large On the blow up phenomena in differential equations and dynamical systems}

\bigskip

%% Author 1:
{\sc Lyudmila Efremova}

%% Address:
{\small\it Nizhniy Novgorod State University, Nizhniy Novgorod 603950, Russia}

%% Email:
{\small\rm lefunn@gmail.com}


\bigskip

%% Author 2:
{\sc Vsevolod Sakbaev}

{\small\it Moscow Institute of Physics and Technology, Dolgoprudny 141700, Russia}

{\small\rm fumi2003@mail.ru}

\end{center}

\bigskip

%% Abstract in English:
The comparison is given of the phenomena of the  $\Omega$-blow up in  dynamical systems and the phenomena of the blow up in the evolution differential equations. The comparison is based on the methods of multivalued analysis. 
\newline
The examples are considered. In particular,  the new example of $C^0$- $\Omega$-blow up in $C^1$-smooth simplest skew products in the plane is described (see \cite{suz06}).
\newline
The procedure is defined of the extension of the dynamical transformation  of the space of the initial conditions of Cauchy problem is the case of the destruction of a solution or in the case of the appearance of the singularities in a finite time (see \cite{TMP}).


\begin{otherlanguage}{russian}

\bigskip

\begin{center}
%% Title in Russian (optional):
{\Large О явлениях взрыва  в дифференциальных уравнениях и динамических системах}
\end{center}

\smallskip

%% Abstract in Russian (optional; could be shorter than English):
С использованием методов многозначного анализа приведено сравнение явления $\Omega$-взрыва
в динамических системах и явления взрыва (или режима с обострением) в
эволюционных дифференциальных уравнениях. 
\newline
Рассмотрены примеры.

\bigskip

\end{otherlanguage}

\begin{thebibliography}{6}

\bibitem{suz06}
E.V.~Blinova, L.S.~Efremova, \emph{On $\Omega $-blow ups in
simplest $C^1$-smooth skew products of maps of an interval}, J. Math. Sci.
\textbf{157} (2009), 456--465.

\bibitem{TMP}
V.Zh.~Sakbaev, \emph{On the averaging of quantum dynamical semigroups}, TMPh. {\textbf{164}} (2010),  455--463.




\end{thebibliography}

\end{document}
