\documentclass[10pt,a4paper]{article}

%% Title/abstract template for the conference in honour of Mark Vishik
%% The original is at http://www.dynamics.iitp.ru/vishik/abstract.tex
%%
%% Instructions:
%% 1. Title and abstract should be in English
%% 2. You are welcome to include the Russian translation (optional).
%%    Russian abstract could be shorter than English.
%% 3. Please make sure that your input, including References, is on one page

%% Enabling Cyrillic input with koi8-r encoding:
\usepackage[T2A]{fontenc}
\usepackage[koi8-r]{inputenc}
\usepackage[russian,english]{babel}

%% Standard packages and definitions:
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsmath}
\def\R{\mathbb{R}}
\def\C{\mathbb{C}}
\def\Z{\mathbb{Z}}
\def\Q{\mathbb{Q}}
\pagestyle{empty}

\begin{document}
\begin{center}

%% Title in English:
{\Large Equation of coagulation process of falling drops}

\bigskip

%% Author 1:
{\sc Hisao Fujita Yashima}

%% Address:
{\small\it Universit\'e 8 Mai 1945, Guelma, Alg\'erie}
{\small\it and}
{\small\it Universit\`a di Torino, Italy}

%% Email:
{\small\rm hisao.fujitayashima@unito.it}

\end{center}

\bigskip

%% Abstract in English:

We consider coagulation process of water drops which 
fall in the air. 
This process is described by an integro-differential 
equation for the density $\sigma (m,t,x)$ of the water 
liquid contained in drops of mass $m$. 
For the motion of drops we consider the their velocity 
$u(m)$ determined by the mass $m$ and the velocity of the 
air; on the other hand for the coagulation process we 
consider a probability $\beta(m_1, m_2)$ of meeting 
between a drop of mass $m_1$ and one of mass $m_2$ 
(see for example \cite{[V84]}). 

First we prove the existence of a stationay solution 
with a constant horizontal wind \cite{[MBAH]}. 
Secondly we prove the existence and uniqueness of the 
global solution in the absence of the wind \cite{[BAH]}; 
the convergence of the global solution to the stationary 
solution is a corollary of this result. 

%% Abstract in Russian (optional; could be shorter than English):

\begin{otherlanguage}{russian}

\bigskip

\begin{center}
%% Title in Russian (optional):
{\Large Уравнение процесса когуляции падающих капель}
\end{center}

\smallskip

Мы рассматриваем процесс когуляции падающих в воздухе 
водяных капель, который описывается интегро-дифференциальным 
уравнением для плотности $\sigma (m,t,x)$ воды, которая 
содержится в каплях массы $m$. 
Для движения капель мы рассматриваем их скорость 
$u(m)$, которое оп\-ре\-де\-ляет\-ся массой $m$ и скоростью 
воздуха, а для процесса когуляции мы рас\-сма\-три\-ваем 
вероятность $\beta(m_1, m_2)$ встречи капли массы 
$m_1$ и капли массы $m_2$ (см. например \cite{[V84]}). 


Во-первых будем доказывать существование стационарного 
решения с постоянным ветром \cite{[MBAH]}. 
Во-вторых будем доказывать существование и един\-ствен\-ность 
глобального решения в отсутствие ветра \cite{[BAH]}; 
отсюда следует также сходимость глобального решения 
к стационарному решению. 

\bigskip

\end{otherlanguage}


\begin{thebibliography}{6}

\bibitem{[BAH]} Belhireche, H., Aissaoui, M. Z., 
Fujita Yashima, H.: Solution globale de l'\'equation de
coagulation des gouttelettes en chute. {\it Quaderno 
Dip. Mat. Univ. Torino, 2012}. 

\bibitem{[MBAH]} Merad, M., Belhireche, H., Fujita Yashima, H.:
Solution stationnaire de l'\'equation de coagulation de
gouttelettes en chute avec le vent horizontal. To 
appear on {\it Rend. Sem. Mat. Univ. Padova}. 

\bibitem{[V84]} V.M. Voloshtchuk, \emph{Kinetic theory of coagulation}.
Gidrometeoizdat, 1984.

\end{thebibliography}


\end{document}
